Should geophysicists use the gravity disturbance or the anomaly?

### 2018-05-24 manuscript/letter.tex
review the sphere code

More often than not, gravity modelling is done by computing the
vertical component of the gravitational acceleration exerted by the sources.
We have shown that, in doing so, one is actually computing the gravity
disturbance while attempting to fit a gravity anomaly.
This is a clear inconsistency.
Doing so may even result in wrong interpretations of a quantitative nature.
In Brazil, for example, the maximum difference
between the gravity disturbance and the free-air anomaly reaches $\approx 9.3$ mGal.
Such difference at the Earth's surface may lead to
an error of $850$ m in the depth-to-center estimate of a sphere with true depth-to-center at $700$ m, radius $699$ m, and density contrast of $600 kg.m^{-3}$.

>>>>

More often than not, gravity modelling is done by computing the
vertical component of the gravitational acceleration exerted by the sources.
We have shown that, in doing so, one is actually computing the gravity
disturbance while attempting to fit a gravity anomaly.
This is a clear inconsistency.
Doing so may even result in wrong interpretations of a quantitative nature.
In Brazil, for example, the maximum difference
between the gravity disturbance and the free-air anomaly reaches $\approx 9.3$ mGal.
Such difference at the Earth's surface may lead to
an error of $850$ m in the depth-to-center estimate of a sphere with true 
depth-to-center at $700$ m, radius $699$ m, and density contrast of $600$ kg~$\cdot$~m~$^{-3}$.
